Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
uppercase

@@

\noindent

@@

\subsection{OpenStack}
\label{sec:openstack}
\begin{itemize}
\item Descripcion basica del openstack (Sisco?)
\end{itemize}

\section{State of Art}
\label{sec:state}
Our solutions
is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines. The solution presented
by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. This one continues without being
integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. On the
other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications.
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

\section{Motivation}
\label{sec:motivation}

@@

\section{Working with AWS}
\label{sec:aws}
In this section, first of all, the current user-level features 
provided by the Amazon Web Services are explained and analyzed 
from the point of view of the GPU usage. 
Finally, the scenarios and experiments where virtualized GPUs are utilized are 
described and first results are showed.

@@

\section{GPGPU Shared Service in OpenStack}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

@@

\section{Discussion}
\label{sec:discussion}
-Volver a hacer un resumen
-posibles futuras aplicaciones (lab)
-pruebas con otros proveedores o con otras plataformas (azure)

\section{Conclusions}
\label{sec:conclusions}

\section{Future work}
\label{sec:future}

@@

=======
\documentclass[a4paper,twoside]{article}

\noindent

\subsection{OpenStack}
\label{sec:openstack}

One of the most prominent open-source cloud computing platform for both private 
and public clouds is OpenStack. The OpenStack project was announced in 2010 by 
Rackspace and NASA, and currently developed and distributed by the OpenStack
Foundation with the support of more than 150 relevant companies. OpenStack is a 
cloud operating system that provides Infrastructure as a Service (IaaS) able to 
control large pools of compute, storage, and networking resources throughout a 
datacenter, all managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.

\section{State of Art}
\label{sec:state}
Our solutions
is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines. The solution presented
by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. This one continues without being
integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. On the
other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications.
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

\section{Motivation}
\label{sec:motivation}

\section{Working with AWS}
\label{sec:aws}
In this section, first of all, the current user-level features 
provided by the Amazon Web Services are explained and analyzed 
from the point of view of the GPU usage. 
Finally, the scenarios and experiments where virtualized GPUs are utilized are 
described and first results are showed.

The first of them was {\it Montecarlo Multigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.

% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:mont-opt}
\end{figure}

Flexibility and economical expenses

\section{GPGPU Shared Service in OpenStack}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

\section{Discussion}
\label{sec:discussion}
-Volver a hacer un resumen
-posibles futuras aplicaciones (lab)
-pruebas con otros proveedores o con otras plataformas (azure)

\section{Conclusions}
\label{sec:conclusions}

\section{Future work}
\label{sec:future}

>>>>

\usepackage{url}% http://ctan.org/pkg/url

@@

%\noindent

@@

\subsection{OpenStack}
\label{sec:openstack}
One of the most prominent open-source cloud computing platform for both private 
and public clouds is OpenStack. The OpenStack project was announced in 2010 by 
Rackspace and NASA, and currently developed and distributed by the OpenStack
Foundation with the support of more than 150 relevant companies. OpenStack is a 
cloud operating system that provides Infrastructure as a Service (IaaS) able to 
control large pools of compute, storage, and networking resources throughout a 
datacenter, all managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.

\section{\uppercase{State of Art}}
\label{sec:state}
Our solutions
is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines. The solution presented
by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. This one continues without being
integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. On the
other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications.
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

\section{\uppercase{Motivation}}
\label{sec:motivation}

@@

\section{\uppercase{Working with AWS}}
\label{sec:aws}
In this section, first of all, the current user-level features 
provided by the Amazon Web Services are explained and analyzed 
from the point of view of the GPU usage. 
Finally, the scenarios and experiments where virtualized GPUs are utilized are 
described and first results are showed.

@@

\section{\uppercase{GPGPU Shared Service in OpenStack}}
In this section all the work related to OpenStack that has been done is explained, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

@@

\section{\uppercase{Discussion}}
\label{sec:discussion}
-Volver a hacer un resumen
-posibles futuras aplicaciones (lab)
-pruebas con otros proveedores o con otras plataformas (azure)

\section{\uppercase{Conclusions}}
\label{sec:conclusions}

\section{\uppercase{Future work}}
\label{sec:future}

@@
